Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-23 manuscript.Rmd
Added Apendix; updated figures; adjusted positioning of sections

@@

```{r fig1, out.width = "400px", fig.cap="Proportions of explained variance in items of personal culture; based on predictions at participants' wave mid-point."}
knitr::include_graphics("fig/variation_share_lm_mdpnt.png")
```

@@

```{r fig2, out.width = "300px", fig.cap="Proportion of explained variance attributable to intrapersonal change; based on predictions at participants' wave mid-point; supressed intercept model; survey indicators not shown."}
knitr::include_graphics("fig/meta_no_int.png")
```

@@

```{r img, out.width = "450px", fig.cap="Proportions of intrapersonal change of explained variance by college degree; based on predictions at participants' wave mid-point."}
knitr::include_graphics("fig/FIG_college2.png")
```

@@

>>>>

\begin{center}
<about here> 
Table 1: The Description of the Data Sources
\end{center}

@@

\begin{center}
<about here>
Figure 1: Proportions of explained variance in items of personal culture; based on predictions at participants' wave mid-point.
\end{center}

@@

\begin{center}
<about here>
Figure 2: Proportion of explained variance attributable to intrapersonal change; based on predictions at participants' wave mid-point; supressed intercept model; survey indicators not shown.
\end{center}

@@

\begin{center}
<about here>
Figure 3: Proportions of intrapersonal change of explained variance by college degree; based on predictions at participants' wave mid-point.
\end{center}

@@

<div id="refs"></div>

\newpage

# Appendix

## Tables

\newpage

## Figures

```{r fig1, fig.height=2, fig.cap="Proportions of explained variance in items of personal culture; based on predictions at participants' wave mid-point."}
knitr::include_graphics("fig/variation_share_lm_mdpnt.png")
```

\newpage
```{r fig2, out.width = "300px", fig.cap="Proportion of explained variance attributable to intrapersonal change; based on predictions at participants' wave mid-point; supressed intercept model; survey indicators not shown."}
knitr::include_graphics("fig/meta_no_int.png")
```

\newpage
```{r fig3, out.width = "450px", fig.cap="Proportions of intrapersonal change of explained variance by college degree; based on predictions at participants' wave mid-point."}
knitr::include_graphics("fig/FIG_college2.png")
```
